Predicting the Housing Market using \\ Linear Regression

### 2023-10-29 manuscript/Manuscript.tex
fixed plot formate
added caption to cat plot

%fix the plot so that it starts with yes each time
\begin{figure}
    \includegraphics[width=1\textwidth]{categorical_plots.pdf}
    \caption{Categorical Variable Plots}
    \label{fig:categorical_plots}
In figure~\ref{fig:categorical_plots}, the plots show the distributions for all the categorical variables.

@@

\begin{figure}

    \includegraphics[width=1\textwidth]{numerical_plots.pdf}
    \caption{Numerical Variable Plots}
    \label{fig:numberical_plots}
\end{figure}

>>>>

\begin{figure}
    \caption{Categorical Variable Plots}
    \includegraphics[width=1\textwidth]{categorical_plots.pdf}
    \label{fig:categorical_plots}
In figure~\ref{fig:categorical_plots}, the plots show the distributions for all the categorical variables. Most of the houses in this data set are located near a main road. Only one-fifth of the houses have a room for guests. For the basement category, two-fifths of them have one. Almost none of the houses have hot water heating. There is air conditioning in about two-fifths of the data. About one-fifth of the houses are located in a preferred area. And lastly, the house can come either furnished, semi-furnished, or unfurnished. Most of the house came semi-furnished, next being unfurnished and then fully furnished.

@@

\begin{figure}
    \caption{Numerical Variable Plots}
    \includegraphics[width=1\textwidth]{numerical_plots.pdf}
    \label{fig:numberical_plots}
\end{figure}
